|

### 2020-11-29 appendix/appendix.Rmd
add table 3
commit 3 11/28

[^mignozzetti]: School of International Relations, Fundação Getulio Vargas, São Paulo, SP, Brazil and Wilf Family Department of Politics, NYU, NY, USA, <umberto.mig@nyu.edu>, <http://umbertomig.com>.

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.

@@

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

@@

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients reported in the studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest $n$, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses 36 estimates, as 10 articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the 126 effect sizes reported in the 26 papers.

@@

Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is 36, while the number of papers is only 26.

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
mod <- update(mod, byvar = aux$elecsys2, print.byvar = F)

mod2 <- tibble(
  TE = mod$TE,
  seTE = mod$seTE,
  studlab = mod$studlab,
  lower = mod$lower,
  upper = mod$upper,
  group = "A") %>%
  bind_rows(.,
            aux = tibble(
              TE = c(mod$TE.random, NA),
              seTE = c(mod$seTE.random, NA),
              studlab = c("Overall Effect", "Prediction Interval"),
              lower = c(mod$lower.random, mod$lower.predict),
              upper = c(mod$upper.random, mod$upper.predict),
              group = "B")) %>%
  group_by(studlab) %>%
  mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
  ungroup()

f1b <- mod2 %>%
  ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
  # Studies coefs
  geom_point(aes(color = group)) +
  # Error Bars
  geom_errorbarh(aes(color = group), height = 0.1) +
  # Colors
  scale_color_manual(values = c("#000000", "#8b0000")) +
  # X-axis limit
  scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
  # Y-axis names
  scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) +
  # Vertical dashed line
  geom_vline(xintercept=0, color="#000000", linetype="dashed") +
  # Labels
  labs(x = "",
       y = "") +
  # Facet - Separating Studies from Overall Effect
  facet_grid(group~., scales = "free", space = "free") +
  # Theme
  theme_minimal() %+replace%
  theme(strip.text.y = element_blank(),
        legend.position = "none",
        axis.text.y = element_text(size = 15, hjust = 1.1),
        axis.text.x = element_text(size = 15, hjust = 1.1))

f1b
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. The majoritarian systems in the sample had a random effects model estimate of -0.25, while the random effects model in the non-majoritarian subgroup fitted a value of 0.08. Both are non-significant, but they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

@@

@@

@@

mod3 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod3_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
    scale_y_discrete(
      labels = function(x) str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

>>>>

[^mignozzetti]: Visiting Assistant Professor, Quantitative Theory and Methods, Emory University, <umberto.mignozzetti@emory.edu>, <http://umbertomig.com>.

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build forest plot for heterogeneous analysis
# Build plot function for forest plots
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```

@@

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since authors use different measures for government spending and the number of lower/upper house members, we extracted all coefficients that provided this information. We decided which variables to keep by following the current practices of the literature. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of `r length(unique(dat$authoryear))` articles.

@@

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 18)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 29)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

@@

The meta-analytic data is comprised of two datasets. The first dataset has the main coefficients reported in the studies. These data include only the most rigorous model from each paper, that is, those estimated with the largest sample size, most control variables, and fixed effects if the authors added them. If the article employed a regression discontinuity design, we chose the coefficient from the optimal bandwidth or from the intermediate one. This sample encompasses `r dim(dat)[1]` estimates, as `r as.numeric(table(table(dat$id))[2])` articles analysed two dependent or independent variables of interest. Our second sample, in contrast, contains all the `r dim(fulldat)[1]` effect sizes reported in the `r length(unique(dat$id))` papers.

@@

Most of papers in our sample analyse the number of legislators in the lower house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[2])`). The second most frequent independent variable is the number of legislators in the upper house (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[1])`). Finally, the minority of papers use the natural log of the number of legislators in the lower house as an independent variable (`r as.numeric(table(unique(select(dat, id, indepvar2))$indepvar2)[3])`). As we noted above, some papers had multiple coefficients, and thus the total number of coefficients is `r dim(dat)[2]`, while the number of papers is only `r length(unique(dat$id))`.

@@

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by electoral system",warning=FALSE, cache=TRUE}
build_forest_het(mod, capt = NULL, hetvar = aux$elecsys2)
```

Therefore, we can see that the hypothesis that majoritarian systems produce systematic positive effects was disproved. Both are non-significant, and they reassure us that the absense of effect is not caused by pooling multiple types of electoral systems.

@@

## Lower House Size and Expenditure per Capita (IV)

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

```{r,include=F,warning=F, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
f8 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
```

### Regression Method Subgroup Analysis

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the expenduture per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (ExpPC), controlling by regression methods",warning=FALSE, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

build_forest_het(mod, capt = NULL, hetvar = aux$method)
```

Although all methods generate a null effect, the IV method seems to be well distributed, with two papers with positive effects and two papers negative displaying negative effects. The random effects model for the subgroup is 0.22, which is negative but non-significant. Improve the estimation technique, for the case of IVs, render still a null effect of legislature size on per capita government expenditure.

## Lower House Size and Log of Expenditure per Capita (RDD Only)

```{r, cache=TRUE}
# Pooling effects analysis -- logExpPC x N (RDD only)
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

```{r,include=F,warning=F, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")
f9 <- build_forest_het(mod, NULL, lsize = 15, ttl = 'Lower House Size and Log of Expenditure per Capita\n(subgrouping by the estimation technique)', hetvar = aux$method)
```

### Regression Method Subgroup Analysis

Over time, the literature evolved to use causally identified techniques for determine the effect of legislature size on the log of expenduture per capita. To study whether the method had an effect on the estimated coefficients, we fit a subgroup analysis using the method employed in each paper.

```{r, fig.width=8, fig.height=6, fig.cap="Subgroup Analysis of (N) x (logExpPC), controlling by the regression methods",warning=FALSE, cache=TRUE}
aux <- dat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC')

mod <- metagen(coef, SE, data=aux,
          studlab=paste(authoryear),
          comb.fixed = FALSE,
          comb.random = TRUE,
          method.tau = "REML",
          hakn = TRUE,
          prediction=TRUE,
          sm="SMD")

build_forest_het(mod, capt = NULL, hetvar = aux$method)
```

For the RDD subgroup analysis, we can see a much clearer picture. All estimates are negative, and the subgroup effect is -0.11. This suggests that improving the estimation renders to a negative result that is likely to hold conditional on more papers using the technique displaying the same effect size and sign.

# Main Graphs Codes

## Figure 1

```{r, echo=T, warning=F, cache=TRUE}
pdf('../graphs/graph1.pdf', width = 16, height = 11)
ggarrange(f1,f3,f5,f4,f6,f2,f7, align = 'hv')
dev.off()
```

## Figure 2

```{r, echo=T, warning=F, cache=TRUE}
pdf('../graphs/graph2.pdf', width = 12, height = 6)
ggarrange(f8, f9, align = 'hv')
dev.off()
```

@@

## Lower House Size and Expenditure per Capita (IV)

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N (IV only)
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'ExpPC',
         method %in% c('IV'))

## Lower House Size and Log of Expenditure per Capita (RDD Only)

```{r, cache=TRUE}
# Pooling effects analysis -- ExpPC x N
aux <- fulldat %>%
  filter(indepvar2 == 'N',
         depvar2 == 'logExpPC',
         method == 'RDD')

@@

mod3 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod3_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

mod4 <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

```{r, warning=F, cache=T}
mod <- permutest(mod, progbar = F, iter = 100)
mod

mod4_permu <- tibble(
  ` ` = c("Intercept",
          "Indepvar: N",
          "Year",
          "Published: No",
          "Elecsys: Non-Majoritarian",
          "Method: Panel",
          "Method: IV"),
  Estimate = mod[["beta"]],
  SE = mod[["se"]],
  `T` = mod[["zval"]],
  `P-Value` = mod[["pval"]],
  CI = paste0("(", round(mod[["ci.lb"]], digits = 4), " ; ",
              round(mod[["ci.ub"]], digits = 4 ), ")"),
  model = "ExpPC - All coefs - Permutation"
) %>%
  mutate_if(is.numeric, list(~round(., digits = 3)))
```

@@

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2, TE),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(-1.1*limg, 1.1*limg)) +
    scale_y_discrete(
      labels = function(x) str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(group~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}

# Build plot function for forest plots to heterogeneous subgroup analysis
build_forest_het <- function(mod, capt, lsize = 22, ttl = NULL, hetvar = NULL) {
  mod <- update(mod, byvar = hetvar, print.byvar = F)

  # Build dataset for plot
  mod2 <- tibble(
    byvar = mod$byvar,
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    arrange(byvar)
  auxmod <- tibble()
  for (i in rev(mod$bylevs)){
    auxmod <- rbind(auxmod, tibble(byvar = i,
                    TE = NA,
                    seTE = NA,
                    studlab = toupper(i),
                    lower = NA,
                    upper = NA,
                    group = "B"))
    auxmod <- rbind(auxmod, 
                    filter(mod2, byvar==i) %>% 
                      arrange(desc(TE)))
    auxmod <- rbind(auxmod, tibble(
      byvar = i,
      TE = mod$TE.random.w[which(mod$bylevs==i)],
      seTE = mod$seTE.random.w[which(mod$bylevs==i)],
      studlab = 'Subgroup Effect',
      lower = mod$lower.random.w[which(mod$bylevs==i)],
      upper = mod$upper.random.w[which(mod$bylevs==i)],
      group = "B"))
  }
  auxmod <- rbind(auxmod, tibble(
    byvar = NA,
    TE = c(mod$TE.random, NA),
    seTE = c(mod$seTE.random, NA),
    studlab = c("Overall Effect", "Prediction Interval"),
    lower = c(mod$lower.random, mod$lower.predict),
    upper = c(mod$upper.random, mod$upper.predict),
    group = "B"))
  mod2 <- data.frame(auxmod)
  mod2$byvar <- toupper(mod2$byvar)
  TEaux <- mod2$TE
  TEaux[mod2$studlab== 'Subgroup Effect'] = TEaux[mod2$studlab== 'Subgroup Effect'] - 100

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab, TEaux),
               x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group),
                   height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits = c(-1.1 * limg, 1.1 * limg)) +
    scale_y_discrete(
      labels = function(x)
        str_replace(x, "_[0-9]*$", "")) +
    geom_vline(xintercept = 0,
               color = "#000000", linetype = "dashed") +
    labs(x = "",
         y = "") +
    facet_grid(byvar~., scales = "free", space = "free") +
    labs(caption = capt,
         title = ttl) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8 * lsize,
                                     hjust = 1),
          axis.text.x = element_text(size = .6 * lsize,
                                     hjust = 1.1),
          plot.caption = element_text(size = lsize),
          plot.title.position = "plot",
          plot.title = element_text(hjust = 0.5,
                                    face = "bold",
                                    margin = margin(0, 0, 10, 0)),
          panel.grid.major = element_blank())
  return(p)
}
```
